Teaching

### 2025-01-06 posts/SP2 Review Response/ReviewResponse.qmd

|     | These seem like opposite results, are they? Is the first result suggesting that network size does not have an effect? More generally, I wonder if we should kick things off with the more basic measures and then lead into the new more comprehensive measures. The story is that social networks are rich constructs with some simpler measures (number of nodes, size, etc.) and some more advanced measures that capture richer dynamics. Part of the contribution is leaning into the richer context and using real time data reveal more insight compared to the simple stuff. Need to tell this story more comprehensively. | Our results show that activating contacts with high K-core can significantly reduce smartphone overuse time, with a more substantial reduction effect on non-communicative use than communication-driven use. Specifically, one standard deviation increase in core number leads to a 5.7-minute decrease in non-communication screen and a 5.34% decrease in overuse rate. However, activating contacts with a high degree centrality does not help curb smartphone overuse. The distinction between the effects of the two features suggests that contacts with a high K-core, which are those embedded in a cohesive group, have a stronger capability to motivate social engagement and project social influence. Furthermore, we find that the size of an activated social network reduces non-communicative screen time but increases communicative screen time. The two types of effects offset each other and result in no significant impact on overall screen time. The two types of effects offset each other and result in no significant impact on overall screen time. Moreover, we find that the impact of social network features does not vary with mobile communication level. Our results reveal that once a cluster of social networks is activated, the communication level does not influence the impact of the activated cluster, even though the activation itself is based on communication events. |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 9   | *"There are generally two types of social isolation: social disconnectedness and perceived isolation. Social disconnectedness refers to the status that someone lacks contacts or social con- nections. "*                                                                                                                                                                                                                                                                                                                                                                                                                         | It is interesting to explore the distinction between social disconnectedness and perceived isolation. In our data, there are three types of perceived loneliness: romantic loneliness, family loneliness and social loneliness. We can use the number of activated contacts per day as a proxy of social disconnectedness. Here is some descriptive results:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     | These are interesting constructs which waiver in their centrality to the story. Do they correlate with our social network measures, are there other measures that capture these distinctions?                                                                                                                                                                                                                                                                                                                                                                                                                                      | The correlation between family loneliness and social disconnectedness:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-8.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-2.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The figure suggests that high family loneliness is correlated with more screen time regardless of the number of contacts activated.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The correlation between romantic loneliness and social disconnectedness:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-9.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-4.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The figure suggests that low romantic loneliness is correlated with high screen time regardless of the number of contacts activated.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The correlation between social loneliness and social disconnectedness:                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-10.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | ![](images/paste-3.png)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    | The figure suggests that high social loneliness is correlated with high screen time when participants' activated contacts are at bottom 20% or top 20%.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: Review Response for Dr.Idris Adjerid

## Dr.Jiayi Liu {#sec-dr.jiayi-liu}

Thank you for your valuable comments and feedback.

+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| No. | Comments                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         | Responses                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
+=====+==================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================+===========================================================================================================================================================================================================================================================================================================================================================================================================================================================================================================+
| 1   | It appears to be that those with higher core-number are mostly close friends. Then one could say that the story is actually much simpler: merely engaging with close friends is what matters. Can you argue for using network features, like core-number, against more intuitive metrics such as contact closeness in this context?                                                                                                                                                                                                                                                                              | Thank you for your constructive comments. We measured the social distance of smartphone users with their contacts, as well as their level of trust in those contacts, which are the common measurement of interpersonal relationships.                                                                                                                                                                                                                                                                    |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | The estimation of the above two constructs suggest that they do not have significant impact on participants smartphone use behavior. Please refer to Table 5:                                                                                                                                                                                                                                                                                                                                             |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | ![](images/close_trust.png){width="35cm"}                                                                                                                                                                                                                                                                                                                                                                                                                                                                 |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| 2   | A fundamental assumption is that social interactions mainly occur through calls and messages. Although the author has presented data showing a link between self-reported interaction levels and observed call/message frequencies, this doesn't establish that calls/messages are the primary channels of interaction. People could have spent more time on other social platforms and offline activities (with the time spent also aligning with the self-reported interaction levels). How do you plan to address these potential unobserved interactions? Or can you justify they don't affect your results? | This is an important issue that we need to address. Thanks for pointing this out. Indeed, there could be unobservable social engagements that are not based on phone call and message: 1) social interactions on other mobile applications; 2) physical interactions that are not based on phone call or messages.                                                                                                                                                                                        |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | First, for the social interactions happening on other platforms, it is indeed unobservable in our data set. However, based on the market share of the most popular mobile messaging channels, our data covered the leading four channels (Whatsapp, Phone calls, Facebook messager and Texting (SMS):![](images/channel.png)                                                                                                                                                                              |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Therefore, we suppose that our data has covered the majority of mobile communication activities.                                                                                                                                                                                                                                                                                                                                                                                                          |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | Second, in terms of the unobserved offline social interactions, there could be two categories:                                                                                                                                                                                                                                                                                                                                                                                                            |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 1.  Smartphone users' offline social interactions were initiated by online communication and then it was swithed to offline social interaction. In this situation , the activation of social network is activated by smartphone communication. This scenario could support our 1 & and 2 hypothesis: activating embedded contacts and interacting with them could facilitate offline social engagement.                                                                                                   |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           |
|     |                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  | 2.  The primary concern is the **offline social interaction is independent of smartphone communication**. In another word, the activation of social network is not based on smartphone communication. Nevertheless, 67.91% (90134/132709) of our observations are in session, which means students are on campus. For those observations, unobserved social interactions within family are ruled out. We speculate that students started with online social engagement except those with their roommates. |
+-----+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
